Supplementary Information to: "Comment on Hodgkins et al. (2018)

### 2023-11-20 analysis/paper/001-reply-main.Rmd
Update figure layout and title.

---
title: 'Supplementary Information to: "The need to reinterpret Hodgkins et al. (2018)"'
author: "Henning Teickner, Klaus-Holger Knorr"
date: ""
output: 
  bookdown::pdf_book:
    keep_tex: true
    citation_package: natbib
    toc: false
bibliography: references
biblio-style: unsrtnat
natbiboptions: super
header-includes:
   - \usepackage{float}
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
fontsize: 12pt
---

@@

# Holocellulose
p1 <- 
  d_poc_latitude_summary %>%
  dplyr::filter(sample_type %in% c("Posterior", "Original") & variable_y == "Holocellulose") %>%
  dplyr::mutate(model = 
                  dplyr::case_when(
                    sample_type == "Posterior" ~ "Modified",
                    sample_type == "Prior" ~ "Prior",
                    sample_type == "Original" ~ "Original"
                  )) %>%
  ggplot() +
  geom_ribbon(aes(x = x_latitude, y = mu_pop_fit, 
                  ymin = mu_pop_lwr, ymax = mu_pop_upr,
                  fill = model), 
              alpha = 0.3) +
  geom_errorbar(data = d_y_yhat_long_sites %>%
                  dplyr::filter(model != "Modified, only MIRS-based" & variable_y == "Holocellulose"), 
                aes(y = fit_mean, x = x_latitude + ifelse(model == "Original", 0, 0.1), 
                    ymin = fit_lwr, ymax = fit_upr),
                colour = "grey", width = 0) +
  geom_path(aes(x = x_latitude, y = mu_pop_fit, colour = model), size = 0.7) +
  geom_point(data = d_y_yhat_long_sites %>%
               dplyr::filter(model != "Modified, only MIRS-based" & variable_y == "Holocellulose"), aes(y = fit_mean, x = x_latitude + ifelse(model == "Original", 0, 0.1), colour = model)) +
  scale_y_continuous(labels = function(x) x * 100) +
  scale_x_continuous(labels = function(x) round(x * x_latitude_scale + x_latitude_center, 0)) +
  labs(x = "Latitude [°]", y = "Content [mass-%]", title = "Holocellulose") +
  theme(legend.position = "bottom")

# Klason lignin
p2 <- 
  d_poc_latitude_summary %>%
  dplyr::filter(sample_type %in% c("Posterior", "Original") & variable_y == "Klason lignin") %>%
  dplyr::mutate(model = 
                  dplyr::case_when(
                    sample_type == "Posterior" ~ "Modified",
                    sample_type == "Prior" ~ "Prior",
                    sample_type == "Original" ~ "Original"
                  )) %>%
  ggplot() +
  geom_ribbon(aes(x = x_latitude, y = mu_pop_fit, 
                  ymin = mu_pop_lwr, ymax = mu_pop_upr,
                  fill = model), 
              alpha = 0.3) +
  geom_errorbar(data = d_y_yhat_long_sites %>%
                  dplyr::filter(model != "Modified, only MIRS-based" & variable_y == "Klason lignin"), 
                aes(y = fit_mean, x = x_latitude + ifelse(model == "Original", 0, 0.1), 
                    ymin = fit_lwr, ymax = fit_upr),
                colour = "grey", width = 0) +
  geom_path(aes(x = x_latitude, y = mu_pop_fit, colour = model), size = 0.7) +
  geom_point(data = d_y_yhat_long_sites %>%
               dplyr::filter(model != "Modified, only MIRS-based" & variable_y == "Klason lignin"), aes(y = fit_mean, x = x_latitude + ifelse(model == "Original", 0, 0.1), colour = model)) +
  scale_y_continuous(labels = function(x) x * 100) +
  scale_x_continuous(labels = function(x) round(x * x_latitude_scale + x_latitude_center, 0)) +
  labs(x = "Latitude [°]", y = "Content [mass-%]", title = "Klason lignin") +
  theme(legend.position = "bottom")

@@

p1 <-
  d_peat_pred_best_latitude_depth %>%
  dplyr::filter(variable_y == "Holocellulose") %>%
  dplyr::mutate(model = ifelse(model == "Best binned spectra", "Modified", model)) %>%
  dplyr::arrange(sample_depth_lower) %>%
  ggplot(aes(y = fit, 
             ymin = lwr,
             ymax = upr,
             x = sample_depth_lower, 
             colour = latitude_class, 
             fill = latitude_class)) +
  geom_hline(yintercept = c(0.11, 0.16, 0.21, 0.37), colour = "grey", linetype = 2) +
  geom_path() +
  geom_ribbon(alpha = 0.2, colour = NA) +
  coord_flip() +
  labs(title = "Holocellulose", 
       y = expression(Holocellulose~content~"[mass-%]"),
       x = "Lower layer boundary depth [cm]") +
  facet_wrap(~ model, 
             scales = "free_y", 
             ncol = 1) +
  scale_x_reverse() +
  scale_y_continuous(labels = function(x) x * 100) +
  guides(colour = guide_legend(title = expression(Latitude>45~degree*N)),
         fill = guide_legend(title = expression(Latitude>45~degree*N)))

p2 <-
  d_peat_pred_best_latitude_depth %>%
  dplyr::filter(variable_y == "Klason lignin") %>%
  dplyr::mutate(model = ifelse(model == "Best binned spectra", "Modified", model)) %>%
  dplyr::arrange(sample_depth_lower) %>%
  ggplot(aes(y = fit, 
             ymin = lwr,
             ymax = upr,
             x = sample_depth_lower, 
             colour = latitude_class, 
             fill = latitude_class)) +
  geom_hline(yintercept = c(0.22, 0.32, 0.35, 0.48), colour = "grey", linetype = 2) +
  geom_path() +
  geom_ribbon(alpha = 0.2, colour = NA) +
  coord_flip() +
  labs(title = "Klason lignin", 
       y = expression(Klason~lignin~content~"[mass-%]"),
       x = "Lower layer boundary depth [cm]") +
  facet_wrap(~ model, 
             scales = "free_y", 
             ncol = 1) +
  scale_x_reverse() + 
  scale_y_continuous(labels = function(x) x * 100) +
  guides(colour = guide_legend(title = expression(Latitude>45~degree*N)),
         fill = guide_legend(title = expression(Latitude>45~degree*N)))

>>>>

---
title: 'Supplementary Information to: "Comment on Hodgkins et al. (2018)"'
author: "Henning Teickner, Klaus-Holger Knorr"
date: ""
output: 
  bookdown::pdf_book:
    keep_tex: true
    citation_package: natbib
    toc: false
bibliography: references
biblio-style: unsrtnat
natbiboptions: super
header-includes:
   - \usepackage{float}
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
fontsize: 12pt
---

@@

# Holocellulose
p1 <- 
  d_poc_latitude_summary %>%
  dplyr::filter(sample_type %in% c("Posterior", "Original") & variable_y == "Holocellulose") %>%
  dplyr::mutate(model = 
                  dplyr::case_when(
                    sample_type == "Posterior" ~ "Modified",
                    sample_type == "Prior" ~ "Prior",
                    sample_type == "Original" ~ "Original"
                  )) %>%
  ggplot() +
  geom_ribbon(aes(x = x_latitude, y = mu_pop_fit, 
                  ymin = mu_pop_lwr, ymax = mu_pop_upr,
                  fill = model), 
              alpha = 0.3) +
  geom_errorbar(data = d_y_yhat_long_sites %>%
                  dplyr::filter(model != "Modified, only MIRS-based" & variable_y == "Holocellulose"), 
                aes(y = fit_mean, x = x_latitude + ifelse(model == "Original", 0, 0.1), 
                    ymin = fit_lwr, ymax = fit_upr),
                colour = "grey", width = 0) +
  geom_path(aes(x = x_latitude, y = mu_pop_fit, colour = model), size = 0.7) +
  geom_point(data = d_y_yhat_long_sites %>%
               dplyr::filter(model != "Modified, only MIRS-based" & variable_y == "Holocellulose"), aes(y = fit_mean, x = x_latitude + ifelse(model == "Original", 0, 0.1), colour = model)) +
  scale_y_continuous(labels = function(x) x * 100) +
  scale_x_continuous(labels = function(x) round(x * x_latitude_scale + x_latitude_center, 0)) +
  scale_color_manual(values = colors_prediction_domain[c(3, 2)]) +
  scale_fill_manual(values = colors_prediction_domain[c(3, 2)]) +
  labs(x = "Latitude [°]", y = "Content [mass-%]", title = "Holocellulose") +
  theme(legend.position = "bottom")

# Klason lignin
p2 <- 
  d_poc_latitude_summary %>%
  dplyr::filter(sample_type %in% c("Posterior", "Original") & variable_y == "Klason lignin") %>%
  dplyr::mutate(model = 
                  dplyr::case_when(
                    sample_type == "Posterior" ~ "Modified",
                    sample_type == "Prior" ~ "Prior",
                    sample_type == "Original" ~ "Original"
                  )) %>%
  ggplot() +
  geom_ribbon(aes(x = x_latitude, y = mu_pop_fit, 
                  ymin = mu_pop_lwr, ymax = mu_pop_upr,
                  fill = model), 
              alpha = 0.3) +
  geom_errorbar(data = d_y_yhat_long_sites %>%
                  dplyr::filter(model != "Modified, only MIRS-based" & variable_y == "Klason lignin"), 
                aes(y = fit_mean, x = x_latitude + ifelse(model == "Original", 0, 0.1), 
                    ymin = fit_lwr, ymax = fit_upr),
                colour = "grey", width = 0) +
  geom_path(aes(x = x_latitude, y = mu_pop_fit, colour = model), size = 0.7) +
  geom_point(data = d_y_yhat_long_sites %>%
               dplyr::filter(model != "Modified, only MIRS-based" & variable_y == "Klason lignin"), aes(y = fit_mean, x = x_latitude + ifelse(model == "Original", 0, 0.1), colour = model)) +
  scale_y_continuous(labels = function(x) x * 100) +
  scale_x_continuous(labels = function(x) round(x * x_latitude_scale + x_latitude_center, 0)) +
  scale_color_manual(values = colors_prediction_domain[c(3, 2)]) +
  scale_fill_manual(values = colors_prediction_domain[c(3, 2)]) +
  labs(x = "Latitude [°]", y = "Content [mass-%]", title = "Klason lignin") +
  theme(legend.position = "bottom")

@@

p1 <-
  d_peat_pred_best_latitude_depth %>%
  dplyr::filter(variable_y == "Holocellulose") %>%
  dplyr::mutate(model = ifelse(model == "Best binned spectra", "Modified model", "Original model")) %>%
  dplyr::arrange(sample_depth_lower) %>%
  ggplot(
    aes(
      y = fit, 
      ymin = lwr,
      ymax = upr,
      x = sample_depth_lower, 
      colour = latitude_class, 
      fill = latitude_class
    )
  ) +
  geom_hline(
    yintercept = c(0.11, 0.16, 0.21, 0.37), 
    colour = "grey", 
    linetype = 2
  ) +
  geom_path() +
  geom_ribbon(alpha = 0.2, colour = NA) +
  coord_flip() +
  labs(
    title = "Holocellulose", 
    y = expression(Holocellulose~content~"[mass-%]"),
    x = "Lower layer boundary depth [cm]"
  ) +
  facet_wrap(~ model, scales = "free_y", ncol = 1) +
  scale_x_reverse() +
  scale_y_continuous(labels = function(x) x * 100) +
  scale_color_manual(values = c("indianred", "dodgerblue")) +
  scale_fill_manual(values = c("indianred", "dodgerblue")) +
  guides(
    colour = guide_legend(title = expression(Latitude>45~degree*N)),
    fill = guide_legend(title = expression(Latitude>45~degree*N))
  ) +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_text(size = 12)
  )

p2 <-
  d_peat_pred_best_latitude_depth %>%
  dplyr::filter(variable_y == "Klason lignin") %>%
  dplyr::mutate(model = ifelse(model == "Best binned spectra", "Modified model", "Original model")) %>%
  dplyr::arrange(sample_depth_lower) %>%
  ggplot(
    aes(
      y = fit, 
      ymin = lwr,
      ymax = upr,
      x = sample_depth_lower, 
      colour = latitude_class, 
      fill = latitude_class
    )
  ) +
  geom_hline(
    yintercept = c(0.22, 0.32, 0.35, 0.48), 
    colour = "grey", 
    linetype = 2
  ) +
  geom_path() +
  geom_ribbon(alpha = 0.2, colour = NA) +
  coord_flip() +
  labs(
    title = "Klason lignin", 
    y = expression(Klason~lignin~content~"[mass-%]"),
    x = "Lower layer boundary depth [cm]"
  ) +
  facet_wrap(~ model, scales = "free_y", ncol = 1) +
  scale_x_reverse() + 
  scale_y_continuous(labels = function(x) x * 100) +
  scale_color_manual(values = c("indianred", "dodgerblue")) +
  scale_fill_manual(values = c("indianred", "dodgerblue")) +
  guides(
    colour = guide_legend(title = expression(Latitude>45~degree*N)),
    fill = guide_legend(title = expression(Latitude>45~degree*N))
  ) +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_text(size = 12)
  )
